---
title: "Final Course Project"
author: "Krishanu Maitra"
date: "18 October 2018"
output: ioslides_presentation
css: mystyle.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Predicting fuel economy for cars | Using the R `mtcars` dataset

* Fuel economy is an essential attribute to consider when we consider buying a car

* In addition to savings, fuel economy of a car also plays an important role in terms of reducing carbon footprint

* Here is a model for predicting the fuel economy of a car based on some of its other attributes which  are readily measurable

* The model is available as a Shiny App for use [here](https://krismaitra.shinyapps.io/finalcp/)

* Information about the data can be found in [R documentation](https://www.rdocumentation.org/packages/datasets/versions/3.5.1/topics/mtcars)

## The model 
* A linear model is created `mpg` is the outcome variable vs. `hp`, `wt` and `am` as predictors

* The model is fitted and its coefficients and their P-values are given as follows:
```{r,echo=TRUE,warning=FALSE,message=FALSE}
library(knitr)
fit <- lm(mpg ~  factor(am) + wt + hp, data = mtcars)
kable(t(summary(fit)$coef)[c(1,4),])
```

Low p values imply that the predictors are significant

## Model characteristics

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(knitr)
y1 <- round(summary(fit)$r.square,3)
y2 <- as.character(pf(summary(fit)$fstatistic[1], summary(fit)$fstatistic[2],
         summary(fit)$fstatistic[3], lower.tail = FALSE))
y3 <- round(summary(fit)$f[1],3)
names(y2) <- ""
d <- data.frame(x = c("R-squared ", "Model p-value", "F-statistic"), y = c(y1,y2,y3), z = c(">0.5,  Good fit", "Low p-value", "Significant, with low p-value, Good fit"))
names(d) <- c("Characteristic", "Value", "Remarks")
kable(d)
```

```{r,echo=FALSE,fig.width=6,fig.height=2.2}
par(mfrow=c(1,2),mar=c(4,4,2,1))
resid <- residuals(fit)
fitted <- fitted.values(fit)
plot(density(resid), xlab = "Residuals", ylab = "Density", main = "Residual distribution")
plot(fitted, resid, xlab = "Predicted values", ylab = "Residuals")
abline(h = 0, col = "red", lty = "dashed")
```

Residual errors in narrow range, almost normally distributed

***
<BR><BR><BR>
The model charactersistics suggest that it is a reasonably good model to predict fuel economy.
<BR><BR>
Please do give it a try.
<BR><BR><BR>
<font color="#5555FF" size="20">Thank you</font>
<BR><BR><BR>
[https://krismaitra.shinyapps.io/finalcp/](https://krismaitra.shinyapps.io/finalcp/)